---
title: "Regression Assignment"
author: "Rizza Pudao"
date: "2023-02-04"
output: html_document
---

##### **Introduction**

This is about regression. we are going to perform regression analysis using marketing data of the datarium package in r.

##### **The Data**

The marketing data has 200 observations and 4 variables namely; youtube, facebook, newspaper, and sales.

```{r echo=FALSE, results='hide'}
library(tidyverse) 
library(caret) 
theme_set (theme_bw())
```

```{r echo=FALSE, results='hide'}
# install datarium if not installed at the console
library(datarium) # loading datarium
```

```{r echo=FALSE, results='markup'}
# load the data
data ("marketing", package = "datarium")
sample_n(marketing, 3)
```

```{r echo=FALSE, results='markup'}
# Split the data into training and test set
set.seed(123)
training.samples <- marketing$sales %>%
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- marketing[training.samples, ]
test.data <- marketing[-training.samples, ]
```

```{r echo=FALSE, results='markup'}
# Build the model
model <- lm(sales ~., data = train.data)
# Summarize the model
summary(model)
# Make predictions
predictions <- model %>% predict(test.data)
# Model performance
# (a) Prediction error, RMSE
RMSE(predictions, test.data$sales)
# (b) R-square
R2(predictions, test.data$sales)
```

```{r echo=FALSE, results='markup'}
# predicting with new data
# using the model
youtube <- 30
facebook <- 45
newspaper <- 13
a <- data.frame (youtube = 30,
                 facebook = 45,
                 newspaper = 13)
a <- data.frame(youtube, facebook, newspaper)
p <- model%>% predict(a)
p
```

our model is as follows:
$$\hat{y} = 3.59 + 0.04x_1 +0.19x_2 + \epsilon$$
where $\hat{y}$is sales, 5x_1 is youtube, 5x_2 is facebook, and $\epsilon$ is the error term.


# ***`Simple linear regression`***

This  shows the estimate of the regression beta coefficients (column Estimate) and their significance levels (column Pr(>|t|). The intercept (b0) is 8.58 and the coefficient of youtube variable is 0.046.


```{r echo=FALSE, results='markup'}
model <- lm(sales ~ youtube, data = train.data)
summary(model)$coef
```
This table shows the predictions on the sales units for two youtube advertising budget: 0 and 1000 made using the R function predict()
```{r echo=FALSE, results='markup'}
newdata <- data.frame(youtube = c(0,  1000))
model %>% predict(newdata)
```

# ***`Multiple linear regression`***
This data illustrates the predictions of sales based on the budget invested in three advertising medias: youtube, facebook and newspaper.

```{r echo=FALSE, results='markup'}
model <- lm(sales ~ youtube + facebook + newspaper, 
            data = train.data)
summary(model)$coef
```

also shows the beta coefficient estimates and their significance levels. 
```{r echo=FALSE, results='markup'}
model <- lm(sales ~., data = train.data)
summary(model)$coef
```

This shows the result of predictions using the R function predict()
```{r echo=FALSE, results='markup'}
# New advertising budgets
newdata <- data.frame(youtube = 30, facebook = 45,
  newspaper = 13)
# Predict sales values
model %>% predict(newdata)
```

# ***`Model summary`***
This summary outputs shows 6 components, including:

##### **1.Call**
it Shows the function call used to compute the regression model.

##### **2. Residuals**
Provide a quick view of the distribution of the residuals, which by definition have a mean zero. Therefore, the median should not be far from zero, and the minimum and maximum should be roughly equal in absolute value.

##### **3.Coefficients**
Shows the regression beta coefficients and their statistical significance. Predictor variables, that are significantly associated to the outcome variable, are marked by stars.

##### **4. Residual standard error (RSE)**

##### **5.R-squared (R2)**

##### **6.F-statistic**
Residual standard error (RSE), R-squared (R2) and the F-statistic are metrics that are used to check how well the model fits to our data.

```{r echo=FALSE, results='markup'}
summary(model)
```

# ***`Coefficients significance`***
This shows the estimate of regression beta coefficients and the associated t-statistic p-values.

```{r echo=FALSE, results='markup'}
summary(model)$coef
```


```{r echo=FALSE, results='markup'}
model <- lm(sales ~ youtube + facebook, data = train.data)
summary(model)
```

# ***`Making predictions`***
This shows predictions using the test data in order to evaluate the performance of our regression model. 
it Predict the sales values based on new advertising budgets in the test data

```{r echo=FALSE, results='markup'}
# Make predictions
predictions <- model %>% predict(test.data)
# Model performance
# (a) Compute the prediction error, RMSE
RMSE(predictions, test.data$sales)
```

The table above shows the computed assessment of the model performance using the prediction error RMSE (Root Mean Squared Error).
 
```{r echo=FALSE, results='markup'}
# (b) Compute R-square
R2(predictions, test.data$sales)
```
The table above  shows the computed assessment of the model performance using the The R-square (R2).

# ***`Plot`***
This shows a linearly increasing relationship between the sales and the youtube variables.
```{r echo=FALSE, results='markup'}
ggplot(marketing, aes(x = youtube, y = sales)) +
  geom_point() +
  stat_smooth()
```











